Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
Add blank line after imports.

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
\begin{verbatim}
    from sklearn.linear_model import LogisticRegression
    clf = LogisticRegression(penalty="l1")
    clf.fit(X_train, y_train)
\end{verbatim}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"}, hence enabling
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C}, which
defines the strength of the regularization) are not explicitly defined and are
thus set to the default values. Upon calling \texttt{fit}, the model is then
learned from the training arrays \texttt{X\_train} and \texttt{y\_train}. Since
all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor. For example, to build a Random Forest on
the same training data, one would simply have to replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by \\
\texttt{RandomForestClassifier()}.

@@

The \textit{predictor} interface defines a \texttt{predict}
method taking as input some new data \texttt{X\_test} and producing as output
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{verbatim}
    y_pred = clf.predict(X_test)
\end{verbatim}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{verbatim}
    from sklearn.cluster import KMeans
    km = KMeans(n_clusters=10)
    km.fit(X_train)
    clust_pred = km.predict(X_test)
\end{verbatim}
In the above example, a \texttt{KMeans} estimator is first fit on the training
data \texttt{X\_train}. Then the \texttt{predict} method is called on the test
data \texttt{X\_test} in order to retrieve predicted cluster labels.
The \texttt{predict} method in \sklearn thus offers a unified way
to compute predictions with respect to unseen data.

@@

Since it is common to modify or filter data before feeding it to a learning
algorithm, some estimators in the library implement a \textit{transformer}
interface which defines a \texttt{transform} method. It takes as input some new
data \texttt{X\_test} and yields as output a transformed version of
\texttt{X\_test}. Preprocessing, feature selection and dimensionality reduction
algorithms are all provided as transformers within the library.  In our example,
if one wanted to preprocess the inputs \texttt{X\_train} before fitting the
logistic regression estimator, e.g., by standardizing the feature values, one
could thus simply write:
\begin{verbatim}
    from sklearn.preprocessing import StandardScaler
    scaler = StandardScaler()
    scaler.fit(X_train)
    X_train = scaler.transform(X_train)
\end{verbatim}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. This can easily be done as follows:
\begin{verbatim}
    X_test = scaler.transform(X_test)
\end{verbatim}
Transformers also include a variety of learning algorithms, such as
dimension reduction (PCA, manifold learning techniques), kernel
approximation techniques, and any other approach that can be used to
derive a modified representation of the data.

>>>>

As an example, let us consider a supervised learning task using logistic regression.
Given the API defined above, solving this problem is as simple as:
\begin{verbatim}
    from sklearn.linear_model import LogisticRegression

    clf = LogisticRegression(penalty="l1")
    clf.fit(X_train, y_train)
\end{verbatim}
In this snippet, a \texttt{LogisticRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{"l1"}, hence enabling
$\ell_1$ regularization. Other hyper-parameters (such as \texttt{C}, which
defines the strength of the regularization) are not explicitly defined and are
thus set to the default values. Upon calling \texttt{fit}, the model is then
learned from the training arrays \texttt{X\_train} and \texttt{y\_train}. Since
all estimators share the same interface, using a different learning algorithm is
as simple as replacing the constructor. For example, to build a Random Forest on
the same training data, one would simply have to replace
\texttt{LogisticRegression(penalty="l1")} in the snippet above by \\
\texttt{RandomForestClassifier()}.

@@

The \textit{predictor} interface defines a \texttt{predict}
method taking as input some new data \texttt{X\_test} and producing as output
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{verbatim}
    y_pred = clf.predict(X_test)
\end{verbatim}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{verbatim}
    from sklearn.cluster import KMeans

    km = KMeans(n_clusters=10)
    km.fit(X_train)
    clust_pred = km.predict(X_test)
\end{verbatim}
In the above example, a \texttt{KMeans} estimator is first fit on the training
data \texttt{X\_train}. Then the \texttt{predict} method is called on the test
data \texttt{X\_test} in order to retrieve predicted cluster labels.
The \texttt{predict} method in \sklearn thus offers a unified way
to compute predictions with respect to unseen data.

@@

Since it is common to modify or filter data before feeding it to a learning
algorithm, some estimators in the library implement a \textit{transformer}
interface which defines a \texttt{transform} method. It takes as input some new
data \texttt{X\_test} and yields as output a transformed version of
\texttt{X\_test}. Preprocessing, feature selection and dimensionality reduction
algorithms are all provided as transformers within the library.  In our example,
if one wanted to preprocess the inputs \texttt{X\_train} before fitting the
logistic regression estimator, e.g., by standardizing the feature values, one
could thus simply write:
\begin{verbatim}
    from sklearn.preprocessing import StandardScaler

    scaler = StandardScaler()
    scaler.fit(X_train)
    X_train = scaler.transform(X_train)
\end{verbatim}
Of course, in practice, it is important to apply the same preprocessing to the
test data \texttt{X\_test}. This can easily be done as follows:
\begin{verbatim}
    X_test = scaler.transform(X_test)
\end{verbatim}
Transformers also include a variety of learning algorithms, such as
dimension reduction (PCA, manifold learning techniques), kernel
approximation techniques, and any other approach that can be used to
derive a modified representation of the data.
